---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statsreportr

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/KyleOfCanada/statsreportr/graph/badge.svg)](https://app.codecov.io/gh/KyleOfCanada/statsreportr)
[![R-CMD-check](https://github.com/KyleOfCanada/statsreportr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/KyleOfCanada/statsreportr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of statsreportr is to make it easy to report the results of statistical analyses in inline code of a R Markdown or Quarto document.

## Installation

You can install the development version of statsreportr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("KyleOfCanada/statsreportr")
```

## Example

Some basic examples which shows you how to generate reports for ANOVAs and t-tests:

```{r example}
library(statsreportr)

# ANOVAs
results <- mtcars |>
  rstatix::anova_test(mpg ~ cyl)

format_p(results$p)

results2 <- mtcars |>
  rstatix::anova_test(mpg ~ cyl * carb)

report_anova(results2)
report_anova(results2, "carb")
report_anova(results2, 2)

# t-tests
results3 <- mtcars |>
  rstatix::t_test(mpg ~ am)

report_t(results3)

results4 <- mtcars |>
  rstatix::t_test(mpg ~ cyl)

cohensd4 <- mtcars |>
  rstatix::cohens_d(mpg ~ cyl)

report_t(results4,
  effect = c("6", "8"),
  cohensd = cohensd4, cohens_magnitude = TRUE
)
```
The intent of this package is to be used inline in a R Markdown or Quarto document. For example, the following inline code:

> ```{block, eval = FALSE}
The results of the t test showed a significant difference in the mpg of 6 vs 8 cylinder cars (`r report_t(results4, effect = c("6", "8"), cohensd = cohensd4, cohens_magnitude = TRUE)`). 
> ```

Will render as:

> The results of the t test showed a significant difference in the mpg of 6 vs 8 cylinder cars (`r report_t(results4, effect = c("6", "8"), cohensd = cohensd4, cohens_magnitude = TRUE)`).
