---
title: "statsreportr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{statsreportr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of statsreportr is to make it easy to report the results of statistical analyses in inline code of a R Markdown or Quarto document.
It is designed to work with the `rstatix` package, but can also use some other inputs, and when rendering to a pdf. The envisioned usecase is to use `rstatix` to perform the statistical tests, and then use `statsreportr` to format the results in a way that is easy to include in a scientific or statistical report.


## Installation

You can install the development version of statsreportr from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("KyleOfCanada/statsreportr")
```

## Examples

Here are examples of the functions in `statsreportr`. In these examples they are outputing to the R console, but they are intended to be used inline in a R Markdown or Quarto document.

```{r setup}
library(statsreportr)

# ANOVAs
results <- mtcars |>
  rstatix::anova_test(mpg ~ cyl)

format_p(results$p)

results2 <- mtcars |>
  rstatix::anova_test(mpg ~ cyl * carb)

results3 <- aov(mpg ~ cyl * carb, data = mtcars)

report_anova(results2)
report_anova(results2, "carb")
report_anova(results2, 2)
report_anova(results3, 2)

# t-tests
results3 <- mtcars |>
  rstatix::t_test(mpg ~ am)

report_t(results3)

results4 <- mtcars |>
  rstatix::t_test(mpg ~ cyl)

cohensd4 <- mtcars |>
  rstatix::cohens_d(mpg ~ cyl)

report_t(results4,
  effect = c("6", "8"),
  cohensd = cohensd4, cohens_magnitude = TRUE
)

# Descriptive stats

mtcars |> report_mean_sd(mpg, cyl, effect = "6")

mtcars |> report_mean_sem(mpg, cyl, effect = "6")
```

When used with inline code in a R Markdown or Quarto document, the following inline code:

> ```{block, eval = FALSE}
The results of the t test showed a significant difference in the mpg of 6 (\``r mtcars |> report_mean_sd(mpg, cyl, effect = "6")`\`) vs 8 ((\``r mtcars |> report_mean_sd(mpg, cyl, effect = "8")`\`)) cylinder cars (\``r report_t(results4, effect = c("6", "8"), cohensd = cohensd4, cohens_magnitude = TRUE)`\`). 
> ```

Will render as:

> The results of the t test showed a significant difference in the mpg of 6 (`r mtcars |> report_mean_sd(mpg, cyl, effect = "6")`) vs 8 (`r mtcars |> report_mean_sd(mpg, cyl, effect = "8")`) cylinder cars (`r report_t(results4, effect = c("6", "8"), cohensd = cohensd4, cohens_magnitude = TRUE)`).

## Functions

The following functions are available in the package:

- `format_p()`: Format p-values to be more readable.
- `report_mean_sd()`: Report the mean and standard deviation of a variable.
- `report_mean_sem()`: Report the mean and standard error of the mean of a variable.
- `report_anova()`: Report the results of an ANOVA test.
- `report_t()`: Report the results of a t-test.
- `report_pc()`: Report the results of a pairwise comparisons test.
- `cor_test()`: Conduct a correlation test.
- `report_cor()`: Report the results of a correlation test.
